\documentclass[11pt,a4paper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\setlist{noitemsep, topsep=0pt}

\begin{document}

\begin{center}
{\LARGE \textbf{Diego Perozo}}\\
\vspace{4pt}
FullStack Developer (Python / Flask / Node.js / Express)\\
Spain \\
\href{mailto:diegodapt18@gmail.com}{diegodapt18@gmail.com} \;|\;
+34 643 891 809 \\
\href{https://linkedin.com/in/diegoperozotroncone}{LinkedIn} \;|\;
\href{https://github.com/dapt4}{GitHub} \;|\;
\href{https://dapt4.github.io/react-portfolio24}{Portfolio}
\end{center}

\section*{Professional Summary}
FullStack Developer with experience building scalable backend systems using Python (Flask, Django, FastAPI) and Node.js (Express). Strong background in REST APIs, microservices, Docker, and Linux environments.

\section*{Technical Skills}
\textbf{Backend:} Python, Flask, Django, FastAPI, Node.js, Express \\
\textbf{Frontend:} React, Angular, Ionic, Vue.js, JavaScript, TypeScript, Sass \\
\textbf{Databases:} PostgreSQL, MySQL, MariaDB, MongoDB \\
\textbf{Architecture:} REST APIs, Microservices \\
\textbf{DevOps:} Docker, Linux, SSH, Redis, Prometheus, Grafana \\
\textbf{Tools:} Git, Bash, Vite \\
\textbf{Methodologies:} Scrum, Kanban

\section*{Experience}

\textbf{Computer Systems Analyst / FullStack Developer} — Ultreya Soluciones S.L. \\
Jun 2025 -- Present
\begin{itemize}
  \item Backend development with Python and Flask.
  \item REST API and microservices implementation.
  \item Frontend development using React.
  \item Docker-based infrastructure and Linux automation.
\end{itemize}

\textbf{Mobile FullStack Developer} — Asesoría y Medios de Gestión S.L. \\
May 2024 -- Jun 2025
\begin{itemize}
  \item Mobile applications with Ionic and Angular.
  \item Backend services using Node.js and Express.
\end{itemize}

\textbf{FullStack Developer} — With Madrid S.L. \\
Dec 2023 -- May 2024
\begin{itemize}
  \item Backend development with Python and Django.
  \item Secure REST API and data models.
\end{itemize}

\textbf{Frontend Developer} — Argotec S.L. \\
Jan 2020 -- Dec 2023
\begin{itemize}
  \item Frontend development with TypeScript and Sass.
  \item Data visualization using maps and charts.
\end{itemize}

\section*{Education}
Backend Development with Python (Django, Flask, FastAPI) — Platzi, 2017 \\
Bachelor of Graphic Design — Universidad Rafael Belloso Chacín, 2014

\end{document}
